Tutorial 2b

### 2025-07-08 Tutorial_2b.Rmd
update Figures 7 and 8 (different linetypes)

```{r epred-grand-plot}
 p1 <- ggplot(epreds_grand, aes(x=timebin, y=.epred, 
                          fill=prime, color=prime)) +
    stat_lineribbon(point_interval="median_qi",
                    alpha = 0.5, 
                    .width = c(.8,.95)) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(x = "time bin", y = "predicted conditional accuracy") #+
    #ggtitle("Average participant")
p1
```

@@

```{r plot-epred-pid}
p2 <- ggplot(epreds_pid, aes(x=timebin, y=.epred, 
                       fill=prime, color=prime)) +
    stat_lineribbon(point_interval="median_qi",
                    alpha = 0.5, 
                    .width = c(.8,.95)) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(x = "time bin", y = "predicted conditional accuracy") +
   # ggtitle("Each participant (N = 6)") +
    facet_wrap(~pid, ncol=3)
p2
```

@@

```{r epred-pid-ame-plot}
p22 <- ggplot(epreds_pid_diffs, aes(x=timebin, y=diff_ca, 
                       fill=contrast, color=contrast)) +
    stat_lineribbon(alpha = 0.5, 
                    point_interval = "mean_qi",
                    .width=c(.8,.95)) +
    #stat_halfeye(point_interval = "mean_qi",.width=c(.8,.95)) +
    geom_hline(yintercept = 0, color = "red", lty = 3) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(-1,1)) +
    labs(x = "time bin", y = "difference in predicted ca") +
   # ggtitle("Subject-specific AMEs") +
    facet_wrap(~pid, ncol=3)
p22
```

>>>>

```{r epred-grand-plot}
 p1 <- ggplot(epreds_grand, aes(x=timebin, y=.epred, 
                          fill=prime, color=prime)) +
    stat_lineribbon(aes(linetype=prime),
                    point_interval="median_qi",
                    alpha = 0.5, 
                    .width = c(.8,.95)) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(x = "time bin", y = "predicted conditional accuracy") #+
    #ggtitle("Average participant")
p1
```

@@

```{r plot-epred-pid}
p2 <- ggplot(epreds_pid, aes(x=timebin, y=.epred, 
                       fill=prime, color=prime)) +
    stat_lineribbon(aes(linetype=prime),
                    point_interval="median_qi",
                    alpha = 0.5, 
                    .width = c(.8,.95)) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(x = "time bin", y = "predicted conditional accuracy") +
   # ggtitle("Each participant (N = 6)") +
    facet_wrap(~pid, ncol=3)
p2
```

@@

```{r epred-pid-ame-plot}
p22 <- ggplot(epreds_pid_diffs, aes(x=timebin, y=diff_ca, 
                       fill=contrast, color=contrast)) +
    stat_lineribbon(aes(linetype=contrast),
                    alpha = 0.5, 
                    point_interval = "mean_qi",
                    .width=c(.8,.95)) +
    #stat_halfeye(point_interval = "mean_qi",.width=c(.8,.95)) +
    geom_hline(yintercept = 0, color = "red", lty = 3) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(-1,1)) +
    labs(x = "time bin", y = "difference in predicted ca") +
   # ggtitle("Subject-specific AMEs") +
    facet_wrap(~pid, ncol=3)
p22
```
